Abstractions for Multi-Sorted Substitutions

### 2023-07-14 paper/paper.tex
Update.

  \subsection{A Structure for Multi-Sorted Syntax}
  The rest of our formalization builds on top of a multi-sorted
  syntax, which we capture in the following structure:
  \LibCode\KTerms
  Aside from capturing our syntactic definitions, we require a proof that the
  variable introduction \texttt{`\_} is injective. This is trivially true
  for all constructors. The instantiation for our System F syntax is straightforward:
  \AppCode\FTerms

@@

  \subsection{Unifying Renamings \& Substitutions}
  A well-known problem with DeBruijn-indices is that full substitution
  cannot be defined directly by structural recursion on the term.
  The usual workaround is to define renamings and substitutions
  separately and use renamings to weaken the terms in substitutions
  when going under binders.

>>>>

  \subsection{A Structure for Multi-Sorted Syntax}
  The rest of our framework builds on top of a multi-sorted
  syntax for which we define the following structure:
  \LibCode\KTerms
  The first three fields record the definitions of sorts, terms, and variable introduction.
  The last field records that variable introduction
  \texttt{`\_} is injective, which is trivially true for
  constructors. The instantiation for our System F syntax is
  straightforward:
  \AppCode\FTerms

@@

  \subsection{Unifying Renamings \& Substitutions}
  A well-known problem with DeBruijn-indices is that the operation of
  applying a substitution \texttt{σ} to a term \texttt{t} cannot be
  defined directly by structural recursion on \texttt{t}.
  If \texttt{t} is a term like \texttt{λx e},
  where the subterm \texttt{e} is under a binder, we need to adjust \texttt{σ}
  for the shifted DeBruijn-indices in \texttt{e}:
  \begin{itemize}
  \item The variable \texttt{zero} refers in \texttt{e} to the variable bound by the binder.
  \item a variable \texttt{suc x} refers to variable \texttt{x} in \texttt{σ}.
  \end{itemize}

  \subsection{Unifying Renamings \& Substitutions}
  A well-known problem with DeBruijn-indices is that full substitution
  cannot be defined directly by structural recursion on the term.
  The usual workaround is to define renamings first and use them
  to weaken the terms in substitutions when going under binders.
